This is a combined template and guideline for writing your project. This template should give the structure and a couple of examples, and it should help you get started on the different chapters of your thesis. You can clone and use this document template (\LaTeX) for your report. You do not need to follow all the guidelines given here, use your own judgment. The idea behind this document is rather to give you a reference for how to set up your document, and what is common to include in the different parts. What follows in this abstract can serve as an example of what will be presented in the other parts too. More information on how to write \LaTeX is given in Chap.~\ref{chap:Theory}, so please go directly to that chapter if you have not written in \LaTeX before.

The abstract is a short summary of your work. It should give the reader enough information to grasp the content of your work and decide whether they want to read it. When you read journal papers, you will see that they are usually just a single paragraph long. For a thesis, the abstract can be somewhat longer, but you should make an effort to try to keep it short and condensed. In general, an abstract should answer most of these questions:
\begin{itemize}
\item Why is the motivation for this work? Why is the study useful?
\item What is the research question? What has been studied?
\item What is(are) the objective(s)?
\item What methodology was used? (What has been done/how was it done?)
\item What are the main results?
\item What are the main conclusions?
\end{itemize}

